---
title: "Regression Models Course Project"
author: "Anikó Medgyesi"
date: '2017 január 8 '
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#MTCars Dataset Analysis
The exercise is about the analysis of MTCars dataset from  Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

1.Is an automatic or manual transmission better for MPG?

2.Quantify the MPG difference between automatic and manual transmissions?

## Dataset description
The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

A data frame with 32 observations on 11 variables.

[, 1]	 mpg	 Miles/(US) gallon
[, 2]	 cyl	 Number of cylinders
[, 3]	 disp	 Displacement (cu.in.)
[, 4]	 hp	 Gross horsepower
[, 5]	 drat	 Rear axle ratio
[, 6]	 wt	 Weight (1000 lbs)
[, 7]	 qsec	 1/4 mile time
[, 8]	 vs	 V/S
[, 9]	 am	 Transmission (0 = automatic, 1 = manual)
[,10]	 gear	 Number of forward gears
[,11]	 carb	 Number of carburetors

Some of the variables should be considered as factors.
```{r cars}
data(mtcars)
mtcars$am <- factor(mtcars$am, levels=c(0,1), labels=c('Automatic', 'Manual'))
mtcars$cyl <- factor(mtcars$cyl)
mtcars$vs <- factor(mtcars$vs)
 mtcars$gear <- factor(mtcars$gear)
 mtcars$carb <- factor(mtcars$carb)

```

## Connection between mpg and transmission.

Based on exploratory data analysis it is seems to be that With manual transmission it is possible to reach a better mpg performance. See appendix.

Let us check with a linear regression model:


```{r model}
fit1 <- lm(mpg ~ am, mtcars)
summary(fit1)
```

We can see on the paremeters of linear modell that there is indeed a relationship between the am and mpg, with a switch to manual transmission it is likely that the mpg will be increased an avareage 7,24 mpg with p-value less then 0.001. The R-squared value 0.3598, so the the modell explains only the 36% of variance. 


## What other parameters should be considered in the model?

```{r model extension}
analysis <- aov(mpg ~ ., data = mtcars)
summary(analysis)
```
The analysis shows that we should integrate into the model the Weight(wt), Displacement(disp), and Number of cilinders(cyl)
The new modell:


```{r model2}
fit2 <- lm(mpg ~ am + cyl + disp + wt, data = mtcars)
summary(fit2)
```
The extended modell explains the 86% of the variance.

The comparision of the two models:

```{r modelcomp}
anova(fit1,fit2)
```
This results in a p-value of 8.637e-08, so we can accept, that the fit2 modell is better then fit1.
So the manual use of gears means  about 1.81 MPG increase. We can trust in our regression models, because our resdidials are approximately normally distributed. (see appendix)

## Appendix
Visualisation for mtcars data:
```{r summary}
summary(mtcars)
require(graphics)
pairs(mtcars, main = "mtcars data")

```

###Visualisation the Miles/gallon(mpg) based on Transmission(am).

```{r mtcars, echo=FALSE}
plot(mpg~am, mtcars, xlab = "Transmission (0 = automatic, 1 = manual)")
```

###Check residuals of fit1 if normally distributed
```{r res1}
par(mfrow = c(2,2))
plot(fit1)
```

###Check residuals of fit2 if normally distributed
```{r res2}
par(mfrow = c(2,2))
plot(fit2)
```